%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 



\documentclass[]{deedy-resume-openfont}


\begin{document}


%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Halie Murray-Davis}{ %\urlstyle{same}\url{http://debarghyadas.com} \\
\href{mailto:halie.murray-davis@students.olin.edu}{halie.murray-davis@students.olin.edu} | 302.752.6372
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Olin College of \\ Engineering}
\descript{BS in Mechanical Engineering}
\location{Expected May 2016 | Needham, MA \\ Cum. GPA: 3.3}
\sectionsep


\sectionsep

\subsection{Worcester Prep}
\location{Grad. May 2012 |  Berlin, Maryland}
\location{Cum. GPA: 3.89}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/hmurraydavis}{\custombold{hmurraydavis}} \\
LinkedIn://  \href{www.linkedin.com/in/hmurraydavis/}{\custombold{hmurraydavis}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}

Mechanics of Solids and Structures \\
Dynamics \\
Mechanical Design \\
Thermodynamics \\
Principles of Engineering \\
Computational Robotics\\
Robotics 1 \\
Integrated Product Design\\
User Oriented Collaborative Design \\
Design Nature \\
Nonlinear Dynamics and Chaos\\
Linearity I \& II\\
Global Management Communications\\
Conflict and Transformation\\
%{\footnotesize \textit{\textbf{Robotics 2 Teaching Assistant}}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Software}
SolidWorks \textbullet{} Subversion \textbullet{} Git \\
Product Data Management (PDM) \\
GNU/Linux \textbullet{} ROS \textbullet{} Adobe Suite
\sectionsep

\subsection{Fabrication}
GMAW Welder \textbullet{} Spot Welder \\
Manual Mill \textbullet{} Laser Cutter \\
3D Printer \textbullet{} CNC Router \\
Thermo Former
\sectionsep

\subsection{Programming}
%\location{Over 5000 lines:}
Python \textbullet{}   MATLAB \textbullet{} Arduino \\
LabVIEW \textbullet{}  \LaTeX\ \\ 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Societites}
ASME \textbullet{} SWE

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Clare Boothe Luce Fellow}
\descript{| Olin Intelligent Vehicles Lab}
\location{June 2014 – May 2015 | Needham, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}\item 
-- Made a land sailing robot to show that land-based test surrogates could be a more effective and efficient way of testing for aquatic robotics. \\
%\item 
-- Quantitatively tested sail luffing sensors to determine the most effective method of sensing when a sail luffs.
%\end{tightemize}
\sectionsep

%\runsubsection{Ether}
%\descript{| Consultant: Engineering Design}
%\location{July 2014 - August 2014 | Needham, MA}
%\begin{tightemize}\item Helped a start-up design the right packaging for their product. 
%\item Developed cost-effective, profit maximizing packaging and products which compel users to try and purchase the product.
%\end{tightemize}
%\sectionsep

\runsubsection{Robotics 2 Course Assistant}
\descript{| Olin College}
\location{January 2014 - May 2014 | Needham, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
Arduino on Arbotix boards, and LabVIEW and Python for high level logic.
%\end{tightemize}
\sectionsep

\runsubsection{3D Printer Assistant}
\descript{| Olin Intelligent Vehicles Lab}
\location{September 2013 - December 2013 | Needham, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}

Helped students design parts for 3D printing, then printed parts for them.
%\end{tightemize}
\sectionsep


\runsubsection{Research Engineer}
\descript{| Olin Intelligent Vehicles Lab}
\location{June 2013 - August 2013 | Needham, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item 
-- Used CNC router to generate CAD and speed design process with 3\textsuperscript{rd} party components.\\
%\item 
-- Mechanically probed objects with CNC router to generate a point cloud that was then input into SolidWorks.
%\item Cut mold for a aquatic robot casing with CNC router.
%\item Designed waterproof sensor suite. 
%\end{tightemize}
\sectionsep

%\runsubsection{TNJ Murray Worldwide Service}
%\descript{| IT, Marketing, \& Sales}
%\location{June 2012 - August 2012 | Dover, DE}
%%\begin{tightemize}
%%\item 
%Developed advertising materials for publication in international periodicals and maintained company's computer network. 
%%\end{tightemize}
%%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Land Sailing Robots as a Test Surrogate}
\descript{| David Barrett}
\location{June 2014 – Present | Needham, MA}
Testing aquatic robotics is expensive, time consuming, and difficult. The software and many mechanical systems required for aquatic robotics can be tested in a land based surrogate. This research focused on providing a test surrogate for sailing, aquatic robots.
\sectionsep

\runsubsection{Sail Luffing Sensors}
\descript{| David Barrett}
\location{Febuary 2014 – Present | Needham, MA}
Quantitatively tested piezoelectric vibration sensors, accelerometers, and pressure sensors for effectiveness as sail luffing sensors. Published.
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%      PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\runsubsection{International Robotic Sailing Conference}
\descript{| 2014}
\location{Piezoelectric Vibrational Sensor for Sail Luffing Detection on Robotic Sailboats}
Halie Murray-Davis and David Barrett \\ 
%Presented paper at conference in Galway, Ireland. 
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership} 
\runsubsection{Microsoft International Women’s Hackathon}
\descript{| 2014}
Lead sub-team planning hackathon and developing materials for hackathon.
\sectionsep

%\runsubsection{Olin Robotic Sailing Sub-team Coordinator}
%\descript{| 2012-2014}
%Lead mechanical sub-team in research of innovative sensing methods for autonomous sail boats. Competed in Int'l Robotic Sailing Regatta in 2013.
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
%\begin{tabular}{rll}
2014	      Clare Boothe Luce Research Fellowship\\
2013	      Aspirations Ambassador, NCWIT National Summit on Women and IT\\
2011          NCWIT National Finalist for Aspirations in Technology
%\end{tabular}
\sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}
